Appendix: Quantitative, Multispecies Monitoring at a Continental Scale

### 2025-02-21 Priors table.tex
Updates from Overleaf

&&\\
&State processes&\\
\hline
$E$ & unknown DNA concentration in copies/$\mu$L & - \\
$D$ & unknown DNA concentration in copies/L & - \\
$F$ & smoothed DNA concentration in copies/L & - \\
&&\\

&Parameters&\\
\hline
$\psi$& mean hake eDNA concentration (copies/$\mu$L) & $\mathcal{N}(2,2)$\\
$\epsilon_{(x,y,d)}$& depth specific random effect & $\mathcal{N}(0,\tau)$\\
$\tau$& standard deviation of depth specific random effect & $\mathcal{N}(0,0.2)$\\
$\delta$& biological replicate random effect & $\mathcal{N}(0,\sigma_D)$\\
$\sigma_D$& standard deviation of biological replicate random effect  & $\mathcal{N}(0,3)$\\
$\phi$& intercept of the qPCR probability of detection relationship & $\mathcal{N}(3,1)$\\
$\beta0$& intercept of the linear relation between the mean Ct values&$\mathcal{N}(39,3)$\\
&and eDNA concentration (K and E) & \\
$\beta1$& slope of the linear relation between the mean Ct values and &$\mathcal{N}(-1.4,0.05)$\\
&eDNA concentration (K and E) & \\
$\gamma0$& intercept of the linear relation between the standard deviation&$\mathcal{N}(0,1)$\\
&of Ct values and eDNA concentration (K and E) & \\
$\gamma1$& intercept of the linear relation between the standard deviation &$\mathcal{N}(0,1)$\\
&of Ct values and eDNA concentration (K and E) & \\
$\alpha$& species amplification efficiency & fixed\\
$\zeta$& ethanol wash effect & fixed\\
&&\\
&Subscripts&\\
\hline
$s$& species ($H$ = Hake) & -\\
$x$& northing & -\\
$y$& easting & -\\
$d$& depth & -\\
$i$& biological replicate & -\\
$r$& technical replicate & -\\
$p$& qPCR plate & -\\
$m$& mock community sample & -\\
$j$& qPCR standard aliquote sample & -\\

@@

mean_hake ~normal(2,2); //global mean hake concentration
log_D_sigma ~ normal(0,3); //variance on log_D_station_depth
log_D_station_depth
logit_phi_0
gamma_1 ~ std_normal();
gamma_0 ~ std_normal();
beta_std_curve_0
beta_std_curve_1
log_D_raw

>>>>

&&\\
&State processes&\\
\hline
$E_{s\neq H}$ & unknown DNA concentration in copies/$\mu$L & $\mathcal{N}(0,5)$\\
$D$ & unknown DNA concentration in copies/L & - \\
$F$ & smoothed DNA concentration in copies/L & - \\
&&\\

&Parameters&\\
\hline
$\psi$& overall mean hake eDNA concentration (copies/$\mu$L) & $\mathcal{N}(2,2)$\\
$\epsilon_{(x,y,d)}$& spatial and depth specific random effect & $\mathcal{N}(0,\sigma_D)$\\
$\sigma_D= (0, +\infty)$& standard deviation of spatial and depth specific random effect & $\mathcal{N}(0,3)$\\

$\delta$& biological replicate random effect & $\mathcal{N}(0,\tau)$\\
$\tau = (0, +\infty)$& standard deviation of biological replicate random effect & $\mathcal{N}(0,0.2)$\\

$\phi$& intercept of the qPCR probability of detection relationship & $\mathcal{N}(3,1)$\\
$\beta0$& intercept of the linear relation between the mean Ct values&$\mathcal{N}(39,3)$\\
&and eDNA concentration (K and E) & \\
$\beta1$& slope of the linear relation between the mean Ct values and &$\mathcal{N}(-1.4,0.05)$\\
&eDNA concentration (K and E) & \\
$\gamma0$& intercept of the linear relation between the standard deviation&$\mathcal{N}(0,1)$\\
&of Ct values and eDNA concentration (K and E) & \\
$\gamma1$& intercept of the linear relation between the standard deviation &$\mathcal{N}(0,1)$\\
&of Ct values and eDNA concentration (K and E) & \\
$\alpha$& species amplification efficiency & fixed\\
$\zeta$& ethanol wash effect & fixed\\
&&\\
&Subscripts&\\
\hline
$s$& species ($H$ = Hake) & -\\
$x$& northing & -\\
$y$& easting & -\\
$d$& depth & -\\
$i$& biological replicate & -\\
$r$& technical replicate & -\\
$p$& qPCR plate & -\\
$m$& mock community sample & -\\
$j$& qPCR standard aliquote sample & -\\

@@
